Transfer Learning in Visual and Relational Reasoning

### 2020-02-05 Transfer_Learning/cvpr_rebuttal/egrebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{7813}
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

\title{Transfer Learning in Visual and Relational Reasoning -- Rebuttal}

\maketitle
\thispagestyle{empty}

\section{Introduction}

{\small
\bibliographystyle{ieee}
\bibliography{}
}

\end{document}

### 2020-02-05 Transfer_Learning/arxiv_version/submission_folder/experiments.tex

\begin{figure*}[htb]
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
	\end{subfigure}%
	\newline
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../results/samnet_cog_orig_hard.png}
	\end{subfigure}%
	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the 
		baseline model~\cite{yang2018dataset} (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
	\label{fig:samnet_cog_detailed}
\end{figure*}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.8\textwidth]{../results/CoGenT_results.pdf}
	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
	\label{fig:CoGenT-results}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.6\textwidth]{../img/architecture/hierarchy}
	\caption{Hierarchy of Task Groups.}
	\label{fig:task-groups}
\end{figure}

@@

The results of these experiments are shown in~\cref{fig:COG-reasoning-results}.
 \begin{figure}[!b]
	\centering
	\includegraphics[width=0.85\textwidth]{../results/COG_reasoning_transfer_v3}
	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
	\label{fig:COG-reasoning-results}
\end{figure}

@@

\begin{figure}[!b]
	\centering
	\includegraphics[width=0.8\textwidth]{../results/samnet_cog_overall_transfer.png}
	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
	\label{fig:samnet_cog_overall_transfer}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.6\textwidth]{../results/CoGenT_B_results.pdf}
	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}
	\label{fig:CoGenT-B-results}
\end{figure}

>>>>

\begin{figure*}[htb]
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/samnet_cog_orig_canonical_no_labels.png}
	\end{subfigure}%
	\newline
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/samnet_cog_orig_hard.png}
	\end{subfigure}%
	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the 
		baseline model~\cite{yang2018dataset} (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
	\label{fig:samnet_cog_detailed}
\end{figure*}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/CoGenT_results.pdf}
	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
	\label{fig:CoGenT-results}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.6\textwidth]{figures/hierarchy}
	\caption{Hierarchy of Task Groups.}
	\label{fig:task-groups}
\end{figure}

@@

The results of these experiments are shown in~\cref{fig:COG-reasoning-results}.
 \begin{figure}[!b]
	\centering
	\includegraphics[width=0.85\textwidth]{figures/COG_reasoning_transfer_v3}
	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
	\label{fig:COG-reasoning-results}
\end{figure}

@@

\begin{figure}[!b]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/samnet_cog_overall_transfer.png}
	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
	\label{fig:samnet_cog_overall_transfer}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.6\textwidth]{figures/CoGenT_B_results.pdf}
	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}
	\label{fig:CoGenT-B-results}
\end{figure}
